---
title: 'Testing: area_extract()'
author: "Dylan"
date: "2025-04-28"
output: html_document
---

```{r lib}
require(rvest)
require(dplyr)
require(stringr)
require(purrr)
require(readr)
require(ggplot2)
require(lubridate)
require(httr)
```

# Overall

This page is just for building and testing `area_extract()`, the overall wrapper function that will automatically:

1. Takes in an area name values in `df_cities`
2. Automatically runs
  - List page download
  - List page parsing
  - List page cleaning
  - List page de-duplication
  - Detail page url sampling
  - Detail page download
  
  
Here's a quick run down of the core extraction flow:

1. `download_list_pages` -> Download the list page and cache to local directory
2. `parse_list_page2` -> Parse the downloaded list page
  |__ `parse_list_page_folder` -> wrapper of `parse_list_page2`, parse all downloaded list page in directory
3. `clean_list_df` -> clean and reformat the values parsed from list page
4. `dedupe_list` -> De-duplicate the rows from cleaned list page values

Part B - Area Detail Page

1. `create_url_list` -> Take the de-duped list, create a list of urls of detail pages to download
2. `download_detail_pages` -> Takes in a vector of urls and download the pages to local directory
3. `parse_detail_page` -> Parse the downloaded detail page
  |__ `parse_detail_page_folder` -> wrapper of `parse_detail_page`, parse all downloaded detail page in directory
4. `clean_detail_df` -> clean and reformat the values parsed from detail page
5. `join_results` -> Combine the data from list pages and detail pages, drop redundant columns



# Getting the summary page info

```{r sub_admin}
df_cities <- read_csv("data/tokyo_wards_and_cities_codes.csv") %>%
  mutate(
    area_code = str_extract(page_url, "(?<=sc=)\\d{5}")
  ) %>%
  arrange(area_code)

```

```{r get_sub_admin_info, cache=TRUE}
hs <- "helper_scripts"
source(file.path(hs, "get_area_page_info.R"))

start_time <- Sys.time()
df_cities_info <- get_area_page_info(data = df_cities)
Sys.time() - start_time
```


```{r}
df_cities_info
```


# Extracting Station


Choose the areas to extract:

```{r}
area_pool <- df_cities %>% #filter(region_en %in% c("Toka")) %>% 
  select(names_en) %>% pull()

message("The Pool: ")
area_pool

message("\n The choice: ")
area_to_extract <- area_pool
area_to_extract


```

Processing time estimate

```{r est_time}
source("helper_scripts/estimate_process_time.R")

sample_levels <- c(0.1, 0.25, 0.5, 0.75, 1.0)

est_time <- estimate_process_time(select_area = area_to_extract,
                      updated_area_info = df_cities_info,
                      sample_parts = sample_levels)
```

```{r est_time}
est_time$detail_table
est_time$sample_parts_time/60

est_complete_time <- Sys.time() + est_time$sample_parts_time['0.1']*60
message(paste0("Est. Complete Time at 10% Sample Level: \n ---", est_complete_time))
```



Take vector of English area names and run the `area_extract()`

```{r, warning=FALSE}
source("helper_scripts/area_extract.R")
area_extract(area_name = area_to_extract,
             overwrite = TRUE, timeout_sec = 5,
             full_process = TRUE,
             sample_part = 0.1, seed = 445856,
             hide_success = TRUE, read_line_notice = 100,
             clean_cache = TRUE, clean_nday_old = NULL,
             run_dt_page_section = TRUE)
```




# Read Extraction Master

```{r}
df_master_log <- read_csv("extraction_job_master_log.csv", show_col_types = FALSE) %>% 
  mutate(
    start_time = with_tz(start_time, tzone = "Asia/Tokyo"),
    end_time = with_tz(end_time, tzone = "Asia/Tokyo")
  )
```


What have we extracted


```{r}
temp <- df_master_log %>% filter(sample_part == 0.25) %>% mutate(area_code = as.character(area_code)) %>%
  select(start_time, area_code, area_name, n_listing_after_deduped, n_detail_success, job_id) %>%
  group_by(area_code) %>%
  slice_max(order_by = start_time)

quick_area_check <- df_cities_info %>% select(names_jp:area_code, max_page) %>%
  mutate(area_code = as.character(area_code)) %>%
  left_join(temp, by = join_by(area_code, names_en == area_name))


```






